---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# userdcm

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/userdcm)](https://CRAN.R-project.org/package=userdcm)
[![R-CMD-check](https://github.com/r-dcm/userdcm/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/r-dcm/userdcm/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/r-dcm/userdcm/branch/main/graph/badge.svg)](https://app.codecov.io/gh/r-dcm/userdcm?branch=main)
<!-- badges: end -->

The goal of userdcm is to ...

## Installation

You can install the development version of userdcm like so:

``` r
# FILL THIS IN! HOW CAN PEOPLE INSTALL YOUR DEV PACKAGE?
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(userdcm)
## basic example code
```

---

## Contributions and Code of Conduct

Contributions are welcome. To ensure a smooth process, please review the [Contributing Guide](https://userdcm.r-dcm.org/CONTRIBUTING.html). Please note that the userdcm project is released with a [Contributor Code of Conduct](https://userdcm.r-dcm.org/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
